### 2017-11-07 Cyber Security/Cyber Security.tex
Cyber Security Notes update

\section{Test}
This is some test text
\paragraph{Test}
How is this

>>>>

\paragraph{IP addresses}
Every computer connected to the internet has an IP Address\\
There are two forms of IP addresses \textbf{IPv4} and \textbf{IPv6}.
\paragraph{IPv6}
IPv6 can support $3.5\times10^{38}$ IP addresses, meaning it is able to accommodate any demand. IPv6 is intended to replace IPv4, however it is taking a long time, the best solution so far is to map all IPv4 addresses to IPv6.
\paragraph{Reserved IP Numbers}
There are many IP addresses reserved for private networks, outside of the internet, for example:
\item 10.0.0.0 to 10.255.255.255
\item 169.254.0.0 to 169.254.255.255
\item 172.16.0.0 to 172.31.255.255
\item 192.168.0.0 to 192.168.255.255
\subsection{DNS}
A DNS translates an readable address(e.g. google.com) to an IP address
